\LARGE \bf \pyRobots{}, a toolset for robot executive control

### 2015-02-27 root.tex
Adaptation to resubmit to IROS

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8
\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

@@

\subsubsection{CoWriter} The {\sc CoWriter} project~\cite{hood2015those}
(Figure~\ref{expe-cowriter}) involves a Nao robot and young students
in a \emph{learning by teaching} interaction: the children have to teach the
robot how to write. This experiment involved a dual ROS/NAOqi environment,
bridged within \pyRobots{}. The high-level behaviour was implemented as a finite
state machine ({\sc smach}) whose states corresponded to \pyRobots{} actions.
While the execution controller was subsequently simplified (towards a tighter
interaction scenario), this illustrates how \pyRobots{}, relying on the
ubiquitous Python language, can possibly blend into and interact with existing
tools.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8
\documentclass[letterpaper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

@@

\subsubsection{CoWriter} The {\sc CoWriter} project~\cite{hood2015when}
(Figure~\ref{expe-cowriter}) involves a Nao robot and young students
in a \emph{learning by teaching} interaction: the children have to teach the
robot how to write. This experiment involved a dual ROS/NAOqi environment,
bridged within \pyRobots{}. The high-level behaviour was implemented as a finite
state machine ({\sc smach}) whose states corresponded to \pyRobots{} actions.
While the execution controller was subsequently simplified (towards a tighter
interaction scenario), this illustrates how \pyRobots{}, relying on the
ubiquitous Python language, can possibly blend into and interact with existing
tools.
